---
title: "lab_report_knapsack"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(knapsackProblem)
```

```{r}
suppressWarnings(RNGversion("3.5.9"))
set.seed(42)
n <- 2000
knapsack_objects <- data.frame(
  w=sample(1:4000, size = n, replace = TRUE),
  v=runif(n = n, 0, 10000)
  )
```

## **What is Package : KnapsackProblem Contains**
This package contain three functions functions to solve Knapsack Problem (refred as KP below): 
**brute_force_knapsack
**dynamic_knapsack
**greedy_knapsack

## **Function brute_force_knapsack()**
This method is solving knapsack problem in serial method but there is an optional parameter parallel (parallel = FALSE) which is by default FALSE and if you pass the value TRUE to this parameter it calculations the combiinations in parallel manner and performance increases exponentially.

<p> The Algorithm can be executed as shown below. The time taken for 16 objects are shown below.

```{r Brute Force Algoritm}
brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500)
profvis::profvis({brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500)})
microbenchmark::microbenchmark(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500))
```

<p> After profiling, it can be seen that it is taking too much time in serial operation, so implemented parallel Brute force and almost 80% increment can be seen. 

```{r Parallel Brute Force Algoritm}
brute_force_knapsack(x = knapsack_objects[1:20,], W = 3500, parallel = TRUE)
profvis::profvis({brute_force_knapsack(x = knapsack_objects[1:20,], W = 3500, parallel = TRUE)})
microbenchmark::microbenchmark(brute_force_knapsack(x = knapsack_objects[1:20,], W = 3500, parallel = TRUE))
```

## **Function Dynamic Knapsack: dynamic_knapsack**
<p> The Algorithm can be executed as shown below. The time taken for 500 objects.
```{r dynamic Knapsack}
dynamic_knapsack(x = knapsack_objects[1:500,], W = 3500)
profvis::profvis({dynamic_knapsack(x = knapsack_objects[1:500,], W = 3500)})
microbenchmark::microbenchmark(dynamic_knapsack(x = knapsack_objects[1:500,],W = 3500))
```

## **Function Greedy Knapsack: greedy_knapsack**
<p> The Algorithm can be executed as shown below. The time taken for 10000 objects.
```{r Greedy Knapsack}
greedy_knapsack(x = knapsack_objects[1:10000,], W = 3500)
microbenchmark::microbenchmark(greedy_knapsack(x = knapsack_objects[1:10000,],W = 3500))
```